
\begin{problem}{AK the Problems}
{stdin}{stdout}
{2 second}{}{}

\Suzukaze, a Codefalser who has the \master title, is now competing in a contest on Codefalses. He has solved all the problems except the last one and there are only ten minutes left. This is a crucial contest to \Suzukaze so he is asking for your help. The problem statement follows:

\par
Two players are given a forest(undirected acyclic graph) and decide to play a game on it. The first player plays first and they take alternating turns. In each turn, the current player can either 1) delete an edge or 2) delete a vertex and the edges on it. Whoever is unable to make a move, loses. Determine who wins if they both play optimally.

\par
If \Suzukaze  solves this last problem and AK the problemset, he will achieve a new title - \grandmaster. However, if he fails on this problem, he will lose all the ratings and stop competing in any contests. Can you help him solve this problem?

\InputFile

The first line contains two integers $n$ and $m$ ($1 \le n \le 10^5,0 \le m \le n-1 $), the number of vertices in the forest and the number of edges in the forest. The vertices in the forest are labeled from 1 to $n$.

In the following $m$ lines, each of the lines contains 2 integers $u, v$ ($1 \le u,v \le n; u \neq v$), which means that there is an undirected edge connecting vertex $u$ and vertex $v$.

It's guaranteed that the input data is a forest.

\OutputFile

If the first player will win the game, output "Suzukaze becomes a grandmaster!" (without quotes). Otherwise, output "Suzukaze loses all his ratings!" (without quotes).

\Examples

\begin{example}
\exmp{
8 6
1 2
2 3
4 5
5 6
6 7
7 8
}{%
Suzukaze loses all his ratings!
}%
\end{example}

\end{problem}
