\begin{problem}{Egma Game}
{stdin}{stdout}
{2 seconds}{}{}

As we all know, \TiChuot is \textit{one of} the greatest professional gamers of all time. And, similar to other great gamers, he loves games,
especially nim games. Today, he just found out an online nim game - Egma. As other nim games, Egma requires proficiency in computing mex values
in order to master it. \TiChuot understands that, just like millions of other games he mastered, Egma requires practicing. This is where his
best friend, \T, comes in to help.\\

\T has prepared a drill for \TiChuot's practice. Initially, \TiChuot is given an array of size $n$ of nonnegative integers $a_1, a_2, ..., a_n$.
Then, \T will give \TiChuot $q$ queries of one of the following types:
    \begin{itemize}
        \item
        $1$ $x$ $v$: Changing $a_x$ to value $v$.
        \item
        $2$ $l$ $r$: Finding the mex of $\{a_l, a_{l + 1}, ..., a_r\}$.
    \end{itemize}
Of course, \TiChuot finished this drill easily. However, he thinks that this challenge can improve, not only his mex-computing skill, but also
his programming skill. Do you also want to give this challenge a try?

\textbf{Note}: Mex value of a set of nonnegative integers is defined to be the minimum nonnegative integer that does not belong to the set.

\InputFile
The first line contains an integer $n$ ($1 \leq n \leq 10^5$), the length of the initial array. The second line contains $n$ integers $a_1, 
a_2, ..., a_n$ ($0 \leq a_i \leq 10^9$). The third line contains an integers $q$ ($1 \leq q \leq 10^5$), the number of queries. Each of the
next $q$ lines contain one query of a type described above:
    \begin{itemize}
        \item
        $1$ $x$ $v$: denotes the first type $(1 \leq x \leq n, 1 \leq v \leq 10^9)$.
        \item
        $2$ $l$ $r$: denotes the second type $(1 \leq l \leq r \leq n)$.
    \end{itemize}

\OutputFile

For each query of the second type, output on one line the answer to such query.

\Examples

\begin{example}
\exmp{
5
1 2 3 4 5
3
2 1 3
1 2 0
2 1 3
}{%
0
2
}%
\end{example}

\end{problem}
